%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% begin week02.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\begin{longtable}{l p{12cm} }
		\logentry{5}{22}{2016}{
			Added more to thesis document.\newline
			\par Worked on singular-value of previous blending equation. where:

\begin{equation*}
\begin{split}
\begin{bmatrix}x_{uv} & 0 \\ 0 & y_{uv}\\\end{bmatrix}
&=
\begin{bmatrix}\mathbf{u} & \mathbf{0} \\ \mathbf{0} & \mathbf{u} \end{bmatrix}^{T}
\begin{bmatrix}\mathbf{M} & \mathbf{0} \\ \mathbf{0} & \mathbf{M} \end{bmatrix}^{T}
\begin{bmatrix}\mathbf{X} & \mathbf{0} \\ \mathbf{0} & \mathbf{Y} \end{bmatrix}
\begin{bmatrix}\mathbf{M} & \mathbf{0} \\ \mathbf{0} & \mathbf{M} \end{bmatrix}
\begin{bmatrix}\mathbf{v} & \mathbf{0} \\ \mathbf{0} & \mathbf{v} \end{bmatrix}
\end{split}
\end{equation*}

where
\begin{equation*}
\begin{split}
%
\mathbf{u} =\begin{bmatrix}u \\ 1\\\end{bmatrix}
\text{, }
%
\mathbf{v} =\begin{bmatrix}v \\ 1\\\end{bmatrix}
\text{, }
%
\mathbf{X} =\begin{bmatrix}x_{00} & x_{01} \\ x_{10} & x_{11}\\\end{bmatrix}
\text{, }
%
\mathbf{Y} =\begin{bmatrix}y_{00} & y_{01} \\ y_{10} & y_{11}\\\end{bmatrix}
\text{, and }
%
\mathbf{M} =\begin{bmatrix}-1 & 1 \\ 1 & 0\\\end{bmatrix}
\end{split}
\end{equation*}
		}
		\logentry{5}{23}{2016}{
Read [Chen1993]~\cite{Chen1993} section 2.4 on \textit{Block Compression}.\newline\par
\SUMMARY{Blocks are established established by \textit{threshold} where each block contains pixels that are \textit{offset by no more than the threshold}, allowing all pixels to be offset at once.}\newline\par
\Kamangar{Doesn't this assume that all pixels in the block have a uniform offset?}\newline\par
Working on MatLab program to perform pixel offsets of corresponding points (i.e. assign corresponding points to pixels in MatLab by non automatic methods) 


		}
		\logentry{5}{24}{2016}{%
			Read following sections from [Chen1993]~\cite{Chen1993}:
			\begin{itemize}
				\item Implementations (3)
				\begin{itemize}
					\item Preprocessing (3.1)
					\item Interactive Interpolation (3.2)
					\item Examples (3.3)
				\end{itemize}
				\item Applications (4)
				\begin{itemize}
					\item Virtual Reality (4.1)
					\item Motion Blur (4.2)
				\end{itemize}
			\end{itemize}
			\quad\par
			\Kamangar{With regards to Section 3.1 and Section 1, why is a graph structure needed? Why is it a lattice?}\newline\par
			\Kamangar{With regards to Section 4.1, I don't understand the concepts of \textit{temporal anti-aliasing} and \textit{super-sampling}?}
		\newline\par
		Made additional changes / added material to thesis document.
		}
		\logentry{5}{25}{2016}{%
Was using figures from \url{http://www.robots.ox.ac.uk/~vgg/hzbook/hzbook2/HZfigures.html} as test images, which may not be best source as there white borders, appear to be up-sampled, and do not contain (extrinsic) calibration info. Consider using images located at \url{http://vision.middlebury.edu/stereo/data/scenes2014/} that contain meta-info including (intrinsic) calibration info.
		}
	\end{longtable}
